---
title: "filter_target_verbs"
output:
  html_document:
    df_print: paged
---

In this script, we will examine the relexive verbs, and filter them to keep only the most relevant.
This results in a much smaller list ready for manual annotation.
Let's take a look at how many truly reflexive verbs we have:

```{r}
library(dplyr)
verbs <- read.csv("target_verbs_all.csv", encoding = "UTF-8")
hist(verbs$refexivity,
     main = "Histogram of reflexivity ratio",
     xlab = "verbs reflexivity",
     ylab = "how many such verbs we have")
```

We can see that most of the 'reflexive' verbs are rarely used in reflexive constructions. 
Some are almost exclusively reflexive. 
Few alternate between reflexive and non-reflexive use (reflexivity between 0.2 and 0.8). These are the relevant verbs.

Let's take a look at how many frequently used verbs we have:

```{r}
hist(verbs$total_frequency, 
     main = "Verb lemmas by frequency",
     xlab = "frequency of lemma",
     ylab = "how many such verbs we have")
```

This graph won't tell us much, but it shows that there are a few verbs with huge frequency but 99.99 percent of verbs have a very low frequency of use. 

We need to get rid of the most frequent verbs, such as modals, to be, to have, and the very rare words:


```{r}
#most reflexive verbs have very low frequency -> are unknown, we exclude them
#few have huge frequency - these are modal verbs, or highly abstact ones (be, have)
freq <- verbs$total_frequency[verbs$total_frequency > 1000]
freq <- freq[freq < 50000]
#there are only a few reflexive verbs, that occur frequently
hist(freq, 
     main = "Verb lemmas by frequency",
     xlab = "frequency of lemma",
     ylab = "how many such verbs we have")
```

Still, it shows that there are only a few reflexive verbs that occur frequently. Most reflexive verbs are rarely used.



Finally, we will filter the verbs:
```{r}
frequent_verbs <- verbs[verbs$total_ipm > 20 & verbs$total_ipm < 100,]
alternating_verbs <- verbs[verbs$refexivity > 0.2 & verbs$refexivity < 0.8,]

filtered_verbs <- merge(frequent_verbs, alternating_verbs, by = "lemma")
filtered_verbs <-
    data.frame(lemma = filtered_verbs$lemma, reflexivity = filtered_verbs$refexivity.x, total_ipm = filtered_verbs$total_ipm.x)
write.csv(filtered_verbs, "target_verbs_filtered.csv", fileEncoding = "UTF-8")
```

