---
title: "gather_results"
output: html_document
---

Let's load the results.

```{r}
library(tidyverse)
library(ggplot2)
result_columns <- c("time", "ip_adress", "controller_name", "item_number", "element_number", "type", "group", "penn_element_type", "penn_element_name", 
                 "parameter", "value", "event_time", "item-correct_answer-comments")

results <- read.csv("results_20210415.csv", header = FALSE, sep="!", encoding = "UTF-8") #use nonexistent separator to put all results into single column
results <- filter(results, !grepl("#", V1)) #filter out comments
results <- separate(results, V1, into = result_columns, sep=",", extra = "merge") #separate into meaningful columns
results <- separate(results, "item-correct_answer-comments", 
                    into=c("item", "correct_answer","sentence", "transitive", "grammatical","comments"), 
                    sep=",", fill = "left") #some rows have extra columns
```

Everything is now stored in a single table with meaningful columns.
How many results do we have?

```{r}
nrow(table(results$ip_adress)) 
nrow(table(results$time))
```

Who are the participants?
```{r}
demographics <- filter(results, penn_element_name=="demographics")
demographics <- data.frame(ip_adress=demographics$ip_adress, parameter=demographics$parameter, value=demographics$value) #relevant columns
demographics_tidy <- spread(demographics, parameter, value) #put variables into columns
demographics_tidy$age <- extract_numeric(demographics_tidy$age)
demographics_tidy <- mutate(demographics_tidy, gender=ifelse(gender == "žena", "F", as.character(gender))) # should change this in the PCIbex script
mean(demographics_tidy$age)
sd(demographics_tidy$age)
```

```{r}
table(demographics_tidy$gender)
table(demographics_tidy$education)
```


Did they leave any comments?

```{r}
comments <- filter(results, parameter=="Final")
```

How many answers in total do we have?

```{r}
judgements <- filter(results, parameter == "Selection", type == "experiment") # multiple choice answers that aren't practice
nrow(judgements)
items_count <- table(judgements$item)
max(items_count)
```
Exclude the non-native participants:

```{r}
non_native_ip <- filter(demographics_tidy, lg == "other")$ip_adress
nonnative_judgements <- filter(judgements, ip_adress %in% non_native_ip)
judgements <- filter(judgements, !(ip_adress %in% non_native_ip))
```


Are the results different for non-native speakers?

```{r}
nonnative_correct <- filter(nonnative_judgements, (value=="positive" & correct_answer==TRUE) | (value=="negative" & correct_answer==FALSE))
nonnative_incorrect <- filter(nonnative_judgements, (value=="positive" & correct_answer==FALSE) | (value=="negative" & correct_answer==TRUE))

nrow(nonnative_correct) / (nrow(nonnative_correct) + nrow(nonnative_incorrect)) * 100
```
Correct ration for non-native speakers

```{r}
judgements$correct <- ifelse((judgements$value=="positive" & judgements$correct_answer==TRUE) | (judgements$value=="negative" & judgements$correct_answer==FALSE), 1, 0)
judgements_agg <- aggregate(judgements$correct, by=list(Category=judgements$ip_adress), FUN=sum)
judgements_agg$correct_ratio <- (judgements_agg$x / 32) * 100
sd(judgements_agg$correct_ratio)
nrow(filter(judgements_agg, correct_ratio==100))
```


How many correct, incorrect and "not sure" answers do we have in total?

```{r}
correct <- filter(judgements, (value=="positive" & correct_answer==TRUE) | (value=="negative" & correct_answer==FALSE))
incorrect <- filter(judgements, (value=="positive" & correct_answer==FALSE) | (value=="negative" & correct_answer==TRUE))

nrow(correct) / (nrow(correct) + nrow(incorrect)) * 100
```

Are the results different for people with reading problems?

```{r}
reading_prob_participants <- filter(demographics_tidy, readingProb == "yes")
reading_prob_judgements <- filter(judgements, ip_adress %in% reading_prob_participants$ip_adress)
reading_prob_correct <- filter(reading_prob_judgements, (value=="positive" & correct_answer==TRUE) | (value=="negative" & correct_answer==FALSE))
reading_prob_incorrect <- filter(reading_prob_judgements, (value=="positive" & correct_answer==FALSE) | (value=="negative" & correct_answer==TRUE))

nrow(reading_prob_correct) / (nrow(reading_prob_correct) + nrow(reading_prob_incorrect)) * 100
```
Correct ratio for each individual

```{r}
judgements$correct <- ifelse((judgements$value=="positive" & judgements$correct_answer==TRUE) | (judgements$value=="negative" & judgements$correct_answer==FALSE), 1, 0)
judgements_agg <- aggregate(judgements$correct, by=list(Category=judgements$ip_adress), FUN=sum)
judgements_agg$correct_ratio <- (judgements_agg$x / 32) * 100
sd(judgements_agg$correct_ratio)
nrow(filter(judgements_agg, correct_ratio==100))
```


For each sentence - how many correct and incorrect judgements do we have?

```{r}
t1 <- data.frame(table(correct$item))
t2 <- data.frame(table(incorrect$item))
correctness_table <- merge(t1, t2, by = "Var1", all = TRUE)
names(correctness_table)[1] <- "sentence"
names(correctness_table)[2] <- "correct"
names(correctness_table)[3] <- "incorrect"
correctness_table$incorrect[is.na(correctness_table$incorrect)] <- 0 # replace NA with 0
correctness_table <- separate(correctness_table, "sentence", c("sentence", "sentence_type"), sep = "_")
#correctness_table <- separate(correctness_table, "sentence_type", c("reflexivity", "grammaticality"), sep = 1)
correctness_table$total <- correctness_table$correct + correctness_table$incorrect
```

Total number of judged sentences, by sentence type

```{r}
sentence_type_agg <- aggregate(correctness_table$total, by=list(Category=correctness_table$sentence_type), FUN=sum)
```


Is probability of incorrect judgment based on sentence type non-random?

```{r}
incorrect <- aggregate(correctness_table$incorrect, by=list(Category=correctness_table$sentence_type), FUN=sum)
chisq.test(incorrect$x)
```
Incorrect judgment rate for ra sentences:



Add reflexivity bias to results:

```{r}
correctness_table$refl_bias <- ifelse(as.numeric(correctness_table$sentence) <= 9 | 
                                          (as.numeric(correctness_table$sentence) >= 17 & 
                                             as.numeric(correctness_table$sentence <= 24)),
                                        "high", "low")
```


Are lemmas with high reflexivity bias more likely to be judged incorrectly in non reflexive sentences?
Are lemmas with low reflexivity bias more likely to be judged incorrectly in reflexive sentences?

```{r}
refl_incorrect <- separate(correctness_table, "sentence_type", c("reflexivity", "grammaticality"), sep = 1)
refl_incorrect$reflexivity <- paste(refl_incorrect$reflexivity, refl_incorrect$refl_bias, sep="_")
refl_incorrect <- filter(refl_incorrect, grammaticality=='G')
refl_incorrect_agg <- aggregate(refl_incorrect$incorrect, by=list(Category=refl_incorrect$reflexivity), FUN=sum)
chisq.test(refl_incorrect_agg$x)
```

```{r}
#high refl. bias verb in reflexive sent or low refl. bias verb in transitive sentence
concordant <- filter(refl_incorrect_agg, Category=="R_high" | Category == "T_low") 
#high refl. bias verb in transitive sentence or low refl. bias verb in reflexive sentence
discordant <- filter(refl_incorrect_agg, Category=="R_low" | Category == "T_high")
```

