---
title: "gather_results"
output: html_document
---

Let's load the results.

```{r}
library(tidyverse)
result_columns <- c("time", "ip_adress", "controller_name", "item_number", "element_number", "type", "group", "penn_element_type", "penn_element_name", 
                 "parameter", "value", "event_time", "item-correct_answer-comments")

results <- read.csv("results_20210127_0910.csv", header = FALSE, sep="!", encoding = "UTF-8") #use nonexistent separator to put all results into single column
results <- filter(results, !grepl("#", V1)) #filter out comments
results <- separate(results, V1, into = result_columns, sep=",", extra = "merge") #separate into meaningful columns
results <- separate(results, "item-correct_answer-comments", into=c("item", "correct_answer", "comments"), sep=",", fill = "left") #some rows have extra columns
```

Everything is now stored in a single table with meaningful columns.
How many results do we have?

```{r}
nrow(table(results$ip_adress)) 
nrow(table(results$time))
```

We have 35 unique IP adresses and 35 unique timestamps. 
That should mean that the are 35 partitcipants and each completed the experiment once.

Who are the participants?
```{r}
demographics <- filter(results, penn_element_name=="demographics")
demographics <- data.frame(ip_adress=demographics$ip_adress, parameter=demographics$parameter, value=demographics$value) #relevant columns
demographics_tidy <- spread(demographics, parameter, value) #put variables into columns
demographics_tidy$age <- extract_numeric(demographics_tidy$age)
demographics_tidy <- mutate(demographics_tidy, gender=ifelse(gender == "žena", "F", as.character(gender))) # should change this in the PCIbex script
mean(demographics_tidy$age)
```
Mean age is 20.5. They are all native speakers of Czech, students of philology.
Some experience reading problems.

Did they leave any comments?

```{r}
comments <- filter(results, parameter=="Final")
```



How many answers in total do we have?

```{r}
scales <- filter(results, parameter == "Choice", type == "experiment") # multiple choice answers that aren't practice
nrow(scales)
```

We have 4480 judged items in total. As expected, each participant judged 128 items (4480 / 35 = 128)
How many correct, incorrect and "not sure" answers do we have?

```{r}
correct <- filter(scales, (value=="dává smysl" & correct_answer==TRUE) | (value=="nedává smysl" & correct_answer==FALSE))
incorrect <- filter(scales, (value=="dává smysl" & correct_answer==FALSE) | (value=="nedává smysl" & correct_answer==TRUE))
not_sure <- filter(scales, value=="nejsem si jistá/ý")
```

There are 4306 correct answers, 122 incorrect and 52 indifferent answers.

What items were incorrectly judged?

```{r}
incorrect_freq <- as.data.frame(table(incorrect$item))
incorrect_freq[order(incorrect_freq$Freq, decreasing = TRUE),]
```

Most were judge incorrectly only once. Reflexive sentences are more problematic. 

In what way were the judgements incorrect?

```{r}
judged_false <- filter(incorrect, value=="nedává smysl")

judged_false_freq <- as.data.frame(table(judged_false$item))
judged_false_freq[order(judged_false_freq$Freq, decreasing = TRUE),]
```

```{r}
judged_true <- filter(incorrect, value=="dává smysl")

judged_true_freq <- as.data.frame(table(judged_true$item))
judged_true_freq[order(judged_true_freq$Freq, decreasing = TRUE),]
```

Reflexive agrammatical sentences are sometimes judged as true, even if they should be false.


Which sentences often receive "i'm not sure" ratings?

```{r}
not_sure_freq <- as.data.frame(table(not_sure$item))
not_sure_freq[order(not_sure_freq$Freq, decreasing = TRUE),]
```

Again, most were confusing to only a single participant. However, RA are sometimes ambivalent.

How often are RA sentences confusing?

```{r}
RA_sentences <- filter(scales, grepl("_RA", item))
RA_correct <- filter(RA_sentences, (value=="dává smysl" & correct_answer==TRUE) | (value=="nedává smysl" & correct_answer==FALSE))
RA_incorrect <- filter(RA_sentences, (value=="dává smysl" & correct_answer==FALSE) | (value=="nedává smysl" & correct_answer==TRUE))
RA_confusing <- filter(RA_sentences, !((value=="dává smysl" & correct_answer==TRUE) | (value=="nedává smysl" & correct_answer==FALSE))) #incorrect or unsure
```

11 percent of these judgements are incorrect or ambivalent
7 percent are incorrect

Let's calculate the reaction times.

```{r}
start_times <- filter(results, value=="Start" & type == "experiment") # start of each experimental item
end_times <- filter(results, value=="End" & type == "experiment") # end of each experimental item
times <- merge(x = start_times, y = end_times, by=c("item", "ip_adress"))
times$difference <- as.numeric(times$event_time.y) - as.numeric(times$event_time.x)
times_simple <- data.frame(ip = times$ip_adress, start=times$event_time.x, end=times$event_time.y, diff=times$difference, item=times$item)
mean(times_simple$diff)
sd(times_simple$diff)
```

Mean reaction time is 4.5 seconds (minus wait time implemented in the experiment)

```{r}
mean(filter(times_simple, grepl("_TG", times_simple$item))$diff)
mean(filter(times_simple, grepl("_TA", times_simple$item))$diff)
mean(filter(times_simple, grepl("_RG", times_simple$item))$diff)
mean(filter(times_simple, grepl("_RA", times_simple$item))$diff)
```

